To assess the stability of the validated model, the validation team performed a
one-at-a-time sensitivity analysis on each continuous predictor. Each predictor
was swept across its observed range while all remaining predictors were held at
their median values. The resulting predicted probability of default is plotted
below.

### Macroeconomic Predictors

@fig-sens-unemployment through @fig-sens-gdp illustrate how the predicted
default probability responds to changes in the macroeconomic environment.

```{r}
#| label: fig-sens-unemployment
#| fig-cap: "Sensitivity of predicted default probability to unemployment rate."

targets::tar_read(sensitivity_plots)[["unemployment_rate"]]
```

```{r}
#| label: fig-sens-cpi
#| fig-cap: "Sensitivity of predicted default probability to Consumer Price Index."

targets::tar_read(sensitivity_plots)[["cpi"]]
```

```{r}
#| label: fig-sens-gdp
#| fig-cap: "Sensitivity of predicted default probability to GDP growth rate."

targets::tar_read(sensitivity_plots)[["gdp_growth"]]
```

### Loan-Level Predictors

@fig-sens-principal through @fig-sens-interest show the model's sensitivity to
loan-level characteristics.

```{r}
#| label: fig-sens-principal
#| fig-cap: "Sensitivity of predicted default probability to principal balance."

targets::tar_read(sensitivity_plots)[["principal_balance"]]
```

```{r}
#| label: fig-sens-credit
#| fig-cap: "Sensitivity of predicted default probability to credit score."

targets::tar_read(sensitivity_plots)[["credit_score"]]
```

```{r}
#| label: fig-sens-dti
#| fig-cap: "Sensitivity of predicted default probability to debt-to-income ratio."

targets::tar_read(sensitivity_plots)[["dti_ratio"]]
```

```{r}
#| label: fig-sens-interest
#| fig-cap: "Sensitivity of predicted default probability to interest rate."

targets::tar_read(sensitivity_plots)[["interest_rate"]]
```

All predictor effects are monotonic and directionally consistent with the model
specification described in [Conceptual Soundness](#sec-conceptual-soundness). The model is most sensitive to **debt-to-income ratio** and **unemployment rate**, and least sensitive to **CPI** and **GDP growth rate**.